### 2024-04-27 author-kit-CVPR2024-v2/sec/1_intro.tex
typo lol

\subsection{Useful Techniques}
\indent Several computer vision techniques offer promising avenues for addressing the challenge of learning 
exercising movements from instructional videos by providing deeper insights into their dynamics and nuances. 
One such technique involves exploring 3D models instead of traditional 2D skeletonization
 methods to create more comprehensive representations of the exercise movements. Unlike 2D skeletonization, 
 which captures only the spatial coordinates of key body joints in a single plane, 3D modeling 
 techniques can capture the full spatial extent of exericse movements, including depth information\cite{Alpher03}. This 
 allows for a more accurate and detailed representation of the individual's body and movements in 
 three-dimensional space, which is particularly valuable for capturing complex and multi-dimensional 
 exercise movements\cite{Authors14b}.
\\
\indent In addition to 3D modeling, other computer vision techniques such as action recognition, pose 
estimation, trajectory analysis, and video segmentation and tracking can provide valuable insights 
into the dynamics of exercise movements. Action recognition algorithms can automatically identify and 
classify different gestures and even exercise sequences, allowing for automated analysis of exercise 
patterns and styles. Pose estimation techniques can accurately estimate the skeletal poses of 
people from video frames, providing a structural representation of their movements that can be 
used for further analysis and interpretation.
\\
\indent Trajectory analysis techniques can track the trajectories of specific body parts or exercise movements 
over time, allowing for the analysis of exercise movement patterns, velocities, and accelerations\cite{Alpher02}. This 
provides valuable insights into the dynamic aspects of these exercises, 
helping learners to better understand the timing and pacing of the movements. Video segmentation and 
tracking methods also serve to segment the videos into individual sequences or movements, allowing for more 
focused analysis and comparison of specific elements.
\\
\indent By leveraging these advanced computer vision techniques, learners can gain a deeper understanding 
of the dynamics and nuances of exercise movements, facilitating more effective learning experiences. 
These techniques can help learners to break down complex movements into smaller, more 
manageable components, identify areas for improvement, and refine their technique with greater 
precision and accuracy. Overall, the integration of computer vision into physical therapy has the 
potential to revolutionize the way patients approach their recovery plan, making it more accessible, engaging, 
and effective for patients of all levels.

>>>>

\subsection{Useful Techniques}
\indent Several computer vision techniques offer promising avenues for addressing the challenge of learning 
exercising movements from instructional videos by providing deeper insights into their dynamics and nuances. 
One such technique involves exploring 3D models instead of traditional 2D skeletonization
 methods to create more comprehensive representations of the exercise movements. Unlike 2D skeletonization, 
 which captures only the spatial coordinates of key body joints in a single plane, 3D modeling 
 techniques can capture the full spatial extent of exercise movements, including depth information\cite{Alpher03}. This 
 allows for a more accurate and detailed representation of the individual's body and movements in 
 three-dimensional space, which is particularly valuable for capturing complex and multi-dimensional 
 exercise movements\cite{Authors14b}.
\\
\indent In addition to 3D modeling, other computer vision techniques such as action recognition, pose 
estimation, trajectory analysis, and video segmentation and tracking can provide valuable insights 
into the dynamics of exercise movements. Action recognition algorithms can automatically identify and 
classify different gestures and even exercise sequences, allowing for automated analysis of exercise 
patterns and styles. Pose estimation techniques can accurately estimate the skeletal poses of 
people from video frames, providing a structural representation of their movements that can be 
used for further analysis and interpretation.
\\
\indent Trajectory analysis techniques can track the trajectories of specific body parts or exercise movements 
over time, allowing for the analysis of exercise movement patterns, velocities, and accelerations\cite{Alpher02}. This 
provides valuable insights into the dynamic aspects of these exercises, 
helping learners to better understand the timing and pacing of the movements. Video segmentation and 
tracking methods also serve to segment the videos into individual sequences or movements, allowing for more 
focused analysis and comparison of specific elements.
\\
\indent By leveraging these advanced computer vision techniques, learners can gain a deeper understanding 
of the dynamics and nuances of exercise movements, facilitating more effective learning experiences. 
These techniques can help learners to break down complex movements into smaller, more 
manageable components, identify areas for improvement, and refine their technique with greater 
precision and accuracy. Overall, the integration of computer vision into physical therapy has the 
potential to revolutionize the way patients approach their recovery plan, making it more accessible, engaging, 
and effective for patients of all levels.
